---
title: "Package -- binomial"
author: "Boris Yung"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{binomial}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---


```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(collaspe = T, coomment = "#>" )
library(binomial)
```

## Calculate Binomial Random Variable
The package *Binomial* is a minimal implementation for calculateing the probailities of random variabl and to visualize the relatvie frequencies in of the random variable. 

## Creating a Binomial random variable
The first step is to create a **binomial variable** object with the function `bin_choose(n,k)` with **n** and **k**. 

  1. n = trials 
  2. k = success

```{r message = FALSE, warning=FALSE}
variable = bin_choose(n = 5,k=2)
variable
```

By defeault, `bin_choose()` creates a _valid_ binomial varialbe with valid `trails`, `success`, **and** `probability`. 

## Calculating the binomial probability
Once you have defined a `"binomial variable"` object, you can use the function `bin_probability(success, trials, prob)` to calculate the _probability_ of `success` in the `number of trials`according to the `probability (probability of success)` you entered. The output will be an object of class `"numeric"`, which will contain the the binomial probability. 
```{r message = FALSE, warning=FALSE}
binpro = bin_probability(success = 2, trials=5, prob=0.5)
binpro
```

## Calculating and plot the binomial distribution
This package can also calculate the `"binomial distribution"` as well. You can use function `bin_distribution(trials,prob)` to create the `"binomial distribution"` in the class of `"bindis"` **and** `"data.frame"`. It will give you a nice table of distribution. 
```{r message = FALSE, warning=FALSE}
bindist = bin_distribution(trials = 5, prob = 0.5)
bindist
```

The `plot()` function will create a nice barplot to display table with class of `"bindis"` that generate from `"bin_distribution"`
```{r message = FALSE, warning=FALSE}
bindistrP = plot(bindist)
bindistrP
```

## Calculating and plot the binomial cumulative distributioon 
You can also calculate the binomial cumulative distribution through this package as well. You can use function `bin_cumulative(trials, prob)` to create a table of `"binomial cumlative distribution"` which is an object of class `"bincum"` **and** `"data.frame"`. 
```{r message = FALSE, warning=FALSE}
bincumu = bin_cumulative(trials = 5, prob = 0.5)
bincumu
```

You can also use the `plot()` function, which can give you a nice line graph that display the table with class `"bincum"` that generated from function `"bin_cumulative"`.

```{r message = FALSE, warning=FALSE}
bincumuP = plot(bincumu)
bincumuP


```



## Listing the variables 
You can use the function `bin_variable(trials, prob)` to generate the numbers of trials and probability of success in a userfriendly, nice formated list. 
```{r message = FALSE, warning=FALSE}
binvar = bin_variable(trials = 10, prob = 0.3)
binvar
```

You can also use the functiono `summary()` to generate the summary of the list with the class of `summary.binvar` which generated from the function `"bin_variable"`. It will give you a nice, customice list that display `mean`, `mode` , `variance`, `skweness` **and** `kurtosis`. 
```{r message = FALSE, warning=FALSE}
binvarsum = summary(binvar)
binvarsum
```

